Causes and effects in Dichotomous Comparative Judgments: an information-theoretical system with plausible mechanism

### 2024-07-26 _tex/index.tex
Built site for gh-pages

>>>>

Graph theory is a branch of mathematics focused on the study of graphs.
Graphs are mathematical structures that model pairwise relations between
objects. They can represent physical relations, such as electrical
circuits and roadways, and less tangible structures, such as ecosystems
and sociological relations\citep{Gross_et_al_2018}. Graphs have proven
useful in various fields, spanning statistics, computer science,
operations research, and the natural and social sciences. One
application in statistics that incorporates concepts from graph theory
is causal inference. Specifically, the structural approach to causal
inference uses directed acyclic graphs (DAG) to provide a formal and
graphical representation of the causal structure of a system
\citep{Neal_2020}.

A graph is a collection of nodes connected by edges. In a directed
graph, edges extend from a \emph{parent} node to a \emph{child} node,
with arrows indicating the direction of the causal influence. Two nodes
that are connected by edge are said to be \emph{adjacent}
\citep{Gross_et_al_2018}. In a directed acyclic graph (DAG), the
direction of causal influences does not loop back on itself, ensuring
that the graph contains no cycles \citep{Neal_2020, McElreath_2020}.
